---
title: "Assignment 4 Pitch"
author: "Lorenzo A Sanchez"
date: "October 2, 2017"
output: ioslides_presentation
---

<style type="text/css">

body, td {
   font-size: 11px;
}
code.r{
  font-size: 11px;
}
pre {
  font-size: 11px
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## "Predict MPG Using Top 3 Predictor Variable Values" Shiny App

This simple app predicts a vehicle's MPG by using the top 3 variables as determined by the stepwise variable selection process and AIC. 

## Variable selection

Below is a summary of the variable selection process using the step() function on the linear model starting with all variables available from the mtcars dataset to predict MPG.

The top 3 predictor variables are:

1. The vehicle having manual transmission or automatic
2. The vehicle's 1/4 mile time in seconds
3. The vehicle's weight in 1000lbs

```{r Stepwise Variable Selection, echo = FALSE, message=FALSE  , warning=FALSE, include= FALSE}

data(mtcars)
lm1 <- lm(mpg~., data = mtcars)
s_lm1 <- step(lm1)
summary(s_lm1)

```

```{r, echo = FALSE, message=FALSE  , warning=FALSE}
summary(s_lm1)

```


## Example of model usage

Below is a sample prediction as produced by the app.

The inputs we will chose are:

- am = 1
- qsec = 18
- wt = 2

Predicted MPG:
```{r cars, echo = FALSE, message=FALSE, warning=FALSE}

model1pred <- predict(s_lm1, newdata = data.frame(am = 1, qsec = 18, wt = 2))
model1pred

```

## Links:

* Shiny App URL:  https://zilben.shinyapps.io/Week_4/
* Shiny App site: https://www.shinyapps.io/admin/#/application/221077
* GitHub repositoty:  https://github.com/zilben/Course-9-Assignment-4/tree/gh-pages
* GitHub Documentation: https://zilben.github.io/Course-9-Assignment-4/index
